\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
riri

In addition to injection attacks, data theft attack is also one of the focuses of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim. In order to mitigate this issue, Meng et al proposed a statistical model using status like GPU/CPU usage to detect JFC attack\cite{meng2018252}.

@@

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.46in] {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\

		\hline 
		USB condom \cite{Condom}& Yes & Yes & Yes & Yes & Yes\\
		\hline 
		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& No & ? & No & No & No\\
		\hline 
		TMSUI\cite{yang2015tmsui}& No & Yes? & No & No & No\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}& No & Yes? & No & No & No\\
		\hline 
		GoodUSB\cite{tian2015defending}& Yes & Yes & Yes? & No & No \\

		\hline
		Neuner et al.\cite{neuner2018usblock}& Yes & No & No & No & depends? \\
		\hline
		Meng et al\cite{meng2018252}& No & No & Yes & No & ?\\
		\hline
	\end{tabular}
	\linebreak
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}

>>>>

In addition to injection attacks, data theft attack is also one of the focuses of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim. In order to mitigate this issue, Meng et al.\cite{JFC} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.

@@

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
		\hline 
		USB condom \cite{Condom}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}, Mohammadmoradi et al\cite{mohammadmoradi2018making}, TMSUI\cite{yang2015tmsui}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ???????? &\circlehalf\\
		\hline 
		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
		\hline

		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline 
		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull means that the defense is effective
	\item[2] \circlehalf means that the defense is partial effective
	\item[3] \circleempty means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}
